---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickform

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

I created this package because I wanted several features not implemented in Google Forms. This is a spin off of the [shinyforms](https://github.com/daattali/shinyforms) package. I wanted survey participants to be able to come back to the survey and edit/change/update their responses and I wanted to be able to have the app email the unique ID that is created for them to allow them to return and edit their responses. This package uses the {googledrive}, {googlesheets4}, and {gmailr} packages to persistently store data as google sheets and email participants. Usually storing credentials and authentication tokens can be tricky in shiny apps so this was designed to hopefully _just work_. You will have to create the app and use it interactively once and do the so-called "OAuth Dance" but then the googleforms package will store the tokens in the '.secrets' folder in the shiny app directory. Make sure to upload that folder when publishing to shinyapps.io. Additionally, to use {gmailr} you will need to set up a 'credentials.json' and manually move it into the shiny app home directory as the app will look for the credentials by using 'credentials.json'. More information on setting up [gmailr here](https://github.com/r-lib/gmailr). Additionally, {quickform} provides convenient wrappers for Shiny widgets that match the names from google forms (i.e shiny::selectInput -> quickform::dropdown).

## Installation

You can install the released version of quickform from GitHub with:

``` r
devtools::install_github('brentscott93/quickform')
``` 

## Examples

This is the code for the example that is currently deployed on shinyapps.io. The responses are saved in a [public Google Drive folder](https://drive.google.com/drive/folders/1sgV9XFyYkf8jGp-xGAHcmIJfN83OkHt9?usp=sharing) under my gmail (brentscott93@gmail.com). I setup credentials for the {gmailr} app so a "returning user ID" can be emailed to the respondents and they can return to update their responses. *Hint: copy/paste of this code will not work for you without first making a credentials to send emails.* 
``` r
quickform(title = "Quickform Demo",
          description = "Description of survey here.",
          questions = list(
                        list(id = "age", type = "numeric", title = "Age (yrs)", required = T),
                        list(id = "height", type = "height", title = "Height (ft-in)", required = T),
                        list(id = "weight_lbs", type = "numeric", title = "Weight (lbs)", required = T),
                        list(id = 'ethnicity', type = "multiplechoice", 
                             title = "Are you of Hispanic, Latino, or of Spanish origin?" , 
                             choices = list('No', 'Yes'), required = T),
                        list(id = "race", type = "multiplechoice", title = "Race", 
                              choices = list( 'American Indian or Alaska Native',
                                              'Asian',
                                              'Black or African American',
                                              'Native Hawaiian or Other Pacific Islander',
                                              'White',
                                              'Other'), 
                              required = T),
                        list(id = "bp_systolic", type = "numeric", title = "Blood Pressure (Systolic)"),
                        list(id = "bp_diastolic", type = "numeric", title = "Blood Pressure (Diastolic)"),
                        list(id = "resting_HR", type = "numeric", title = "Resting Heart Rate")
                        ),

                        gmail = T,
                        folder = 'quickform-demo',
                        returningUser = T,
                        emailId = T,
                        subject = 'Quickform Demo Email ID'

)
```

```{r}
knitr::include_app("https://brentscott93.shinyapps.io/quickform/")
```

